Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
Begin of introduction

@@

\section{Problem formulation}

@@

\subsection{Probabilistic planning}

\subsection{Replanning}
\begin{itemize}
	\item Describe the determinization, or explain
\end{itemize}

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem (usefull for modelling nearly inifinite processes)
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
	\item The challenge or large branching factors (induced by natural dynamic)
\end{itemize}

\section{Domain description}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions. We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test. This paper concludes on evaluation both planners using the translated domains.

\subsection{Interesting domains}
The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty. The baseline test evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.

\subsection{Real world evaluation}

Explain shortcomings

\subsection{Probabilistically interesting domains}
A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:

@@

@@

\section{Theoretical approach}

\begin{itemize}
	\item Describe how we are using the created domain
	\item show pseudo code for the 2 papers
	\item Introduce the improvements (or combination) of the approaches of the papers fitted for the domain
\end{itemize}

@@

\section{Empirical evaluation}

@@

\section{Related Work}
% Use related work to display the differences with own work

@@

%---------------------------------------------------------------------------------------------------------------------------

@@

The following structural properties are identified for comparing probabilistic planning with replanning:
\begin{itemize}
	\item 'dead' end states
	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
	\item number of distinct trajectories
	\item presence of mutual exclusion
\end{itemize}

@@

Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate. A replanner can also perform optimally for probabilistically interesting planning problems whenever the 'most promising' goal trajectory is the correct thing to do. They create several domains to explore the issue of replanning vs. probabilistic planning.

>>>>

Since the first incorporation of the International Probabilistic Planning
Competition (IPPC), it has undergone radical changes. Dominating planners
of previous incorporations had a strong focus on goal-oriented MDPs,
determinizing and using powerful classical planners (e.g. FF
\cite{Hoffmann01theff}).New benchmarks have demonstrated weaknesses in existing
solution techniques.

@@

\section{Problem Formulation}

\subsection{Markov Decision Process}

\subsubsection{Goal-oriented MDPs}

\subsubsection{MDP with Finite Horizon}

\subsection{Planners}

@@

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
	\item The challenge or large branching factors (induced by natural dynamic)
\end{itemize}

\subsection{Probabilistic Interestingness}

Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions. We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test. This paper concludes on evaluation both planners using the translated domains.

The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty. The baseline test evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.

Following existing domains were said to be probabilistically interesting:

\begin{itemize}
	\item Drive
	\item Exploding blocksworld
	\item Pitchcatch
	\item Schedule
	\item Tireworld
\end{itemize}

@@

\section{Domain Descriptions}

\subsection{IPPC-2011 Domains}

\subsection{Real-World Domains}

\subsection{Baseline test for Probabilistic Interesting domains}

@@

\section{Planners}

\subsection{FF-Replan}

\subsection{Gourmand}

@@

\section{Future Experiment}

\subsection{Setup}

\subsection{FF-Replan}

\subsubsection{FF-Replan with Finite Horizon}

\subsection{Hypothesis}

@@

\section{Related Work}

\subsection{RFF}

\subsection{PROST}

\subsection{FF-H+}

% Use related work to display the differences with own work

@@

@@

The following structural properties are identified for comparing probabilistic planning with replanning:
\begin{itemize}
	\item `dead' end states
	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
	\item number of distinct trajectories
	\item presence of mutual exclusion
\end{itemize}

@@

Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate. A replanner can also perform optimally for probabilistically interesting planning problems whenever the `most promising' goal trajectory is the correct thing to do. They create several domains to explore the issue of replanning vs\@. probabilistic planning.
